---
title: "Followup"
author: "Ziwei Zhang"
date: '2022-05-25'
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(plyr)
library(dplyr)
library(lme4)
library(ggeffects)
library(ggplot2)
library(tidyr)
library(lmerTest)
library(sjstats)
library(rstatix)
library(afex)
library(emmeans)
```

```{r}
multiple.func <- function(x) {
      read_csv(x, col_types = cols(yoke_participant = col_character()))
}
```


```{r}
#setwd("/Users/ziweizhang/Downloads/followup/")
#file_list <- list.files()

# read files in the output directory, concatenate
data_all <- list.files(path = "/Users/ziweizhang/Downloads/followup/",  # Identify all CSV files
                       pattern = "*.csv", full.names = TRUE) %>% 
  lapply(multiple.func) %>%                              # Store all files in list
  bind_rows                                         # Combine data sets into one data set 
as.data.frame(data_all) 

```
#
```{r}
df_ordered <- read.csv('/Users/ziweizhang/Downloads/Stats_lr_trig_data/analysis_output/E2/TD_lmm_E2.csv')
# %>%
#       mutate(participant = as.factor(participant),
#            attention_state = as.factor(attention_state),
#            within_triplet_counter = as.factor(within_triplet_counter),
#            within_stream_position = as.factor(within_stream_position))
df_ordered$within_triplet_counter = as.factor(df_ordered$within_triplet_counter )
df_ordered$within_stream_position = as.factor(df_ordered$within_stream_position )
df_ordered$participant = as.factor(df_ordered$participant)
df_ordered$attention_state = as.factor(df_ordered$attention_state)

contrasts(df_ordered$within_triplet_counter) <- contr.treatment(base = 2, n = 3)
contrasts(df_ordered$within_stream_position) <- contr.treatment(base = 4, n = 6)

model_residual_from_stream = lmer(TD_rt ~ within_stream_position + (1 | participant), data=df_ordered)
df_ordered$resid_from_stream<-resid(model_residual_from_stream)
df_ordered$resid_from_stream<-resid(model_residual_from_stream)
```


# Attention check and exclusion criteria
```{r}
question = data_all %>% subset(is.na(responses) ==  F)
question
#locate answer of attention check question and perform exclusion
attention_check = question %>% subset(is.na(participant) ==  F)
attention_check
#answers to the second question are all SPACEBAR
```

# Target detection
```{r}
# test_part with post_TD tag are the trials of interests
post_TD_raw = data_all %>% subset(test_part == 'post_TD')
post_TD_raw 
```

```{r}
#read recreate.csv to find the regular triplet for both attentional states, match that with yoke participant
recreate_template <- read.csv('/Users/ziweizhang/Downloads/Stats_lr_trig_data/analysis_output/E2/recreate.csv') %>%
      mutate(yoke_participant_template = as.factor(participant))
recreate_template <- recreate_template[, c('yoke_participant_template','fast_triplet','slow_triplet')]
recreate_template
```

```{r}
sub_id_collected <- unique(data_all$participant)
yoke_id_collected <- na.omit(unique(data_all$yoke_participant))
yoke_id_collected <- rapply(list(yoke_id_collected),function(x) ifelse(x=="8640000000","864e7",x), how = "replace")

yoke_id_template <- unique(recreate_template$yoke_participant_template)
setdiff(unlist(yoke_id_collected),unlist(yoke_id_template))
```


```{r}
length(sub_id_collected)
length(unlist(yoke_id_collected))
length(yoke_id_template)
```


```{r}
post_TD_raw$participant <- as.factor(post_TD_raw$participant)
post_TD_raw$attention_state <- as.factor(post_TD_raw$attention_state)
post_TD_raw$TD_within_triplet_counter <- as.factor(post_TD_raw$TD_within_triplet_counter)
post_TD_raw =post_TD_raw[,c("participant", "TD_trial_number", "TD_target_position", "TD_rt","attention_state","TD_within_triplet_counter","test_part")]
post_TD_raw
print(length(unique(post_TD_raw$participant)))
```

```{r}
#unique(post_TD$TD_within_triplet_counter)
#is.nan(post_TD[['TD_within_triplet_counter']])
post_TD_raw[is.nan(post_TD_raw$TD_within_triplet_counter), ]
unique(post_TD_raw$attention_state)
```

# Exlcude outliers
```{r}
#detach("package:plyr")
nan_mean <- function(x) mean(na.omit(x))
post_TD <- post_TD_raw %>% 
               group_by(participant) %>% 
               filter(abs(TD_rt - nan_mean(TD_rt)) <= (sd(TD_rt, na.rm = TRUE) * 3))
```

# TD RT distribution
```{r}
(nan_mean(post_TD$TD_rt))
(sd(post_TD$TD_rt, na.rm = TRUE))
```

```{r}
mean_post_TD_RT <- post_TD %>% group_by(TD_trial_number) %>% summarise(mean_rt = nan_mean(TD_rt))
mean_post_TD_RT
```


```{r}
y_max <- max(post_TD$TD_rt) + 1

p_rt_dist <- ggplot(post_TD,aes(x=TD_rt)) +
    geom_histogram(alpha=0.7, bins = 25, color="#B4B4B4", fill="light gray") +
    theme_classic() + theme(aspect.ratio = 0.8, legend.position="right", axis.text.y=element_text(size=14), axis.text.x=element_text(size=14,colour = "black"), axis.title.y=element_text(size=14,colour = "black"),axis.title.x=element_text(size=14), legend.direction = "vertical", legend.text=element_text(size=14)) +
    guides(fill = guide_legend(label.position = "top")) +
  labs(x = "E2 TD RT(ms)", y = "count", fill = "") + scale_y_continuous(breaks = seq(0, y_max, by = 250))
#layer_scales(p_rt_dist)$y$range$range

#ggsave("SuppFig_5b.pdf", width = 5.5, height = 4, dpi=300)
p_rt_dist
```
# Distribution fit
```{r}
library(fitdistrplus)
normal_dist <- fitdistrplus::fitdist(post_TD$TD_rt, "norm")
plot(normal_dist)

lognorm_dist <- fitdistrplus::fitdist(post_TD$TD_rt, "lnorm")
plot(lognorm_dist)

gamma_dist <- fitdistrplus::fitdist(post_TD$TD_rt, "gamma")
plot(gamma_dist)

gofstat(list(gamma_dist, normal_dist,lognorm_dist), fitnames = c("gamma", "norm","lnorm"))
```
```{r}
norm_dist <-  fitdistrplus::fitdist(post_TD$TD_rt, "norm")
#pdf(file="SuppFig_7.pdf") #, width = 5.5, height = 4, dpi=300
plot(norm_dist)
dev.off()
```

# Run lmer models
```{r}
model_4_followup = lmer(TD_rt ~ TD_within_triplet_counter * attention_state + (attention_state + TD_within_triplet_counter|participant), data=post_TD)
Anova(model_4_followup)
```


```{r}
post_TD_nonan = na.omit(post_TD)
model_residual_from_stream = lmer(TD_rt ~ TD_target_position + (1 | participant), data=post_TD_nonan)
post_TD_nonan$resid_from_stream<-resid(model_residual_from_stream)
```

```{r}
#contrasts(df_ordered$within_triplet_counter) <- contr.treatment(base = 2, n = 3)
model_5_followup = lmer(resid_from_stream ~ TD_within_triplet_counter * attention_state + (attention_state + TD_within_triplet_counter|participant), data=post_TD_nonan)
# model_5 = glmer(resid_from_stream ~ within_triplet_counter * attention_state + (1 | participant), data=df_ordered, family = gaussian(link = "identity"))
Anova(model_5_followup)
chi_sqrt_E1b <- Anova(model_5_followup)[3,'Chisq']
chi_sqrt_E1b
```


```{r}
#summary(model_5)
#anova(model_5)
```


# Plot
```{r}
nan_se <- function(x) sqrt(var(x,na.rm=TRUE) / length(na.omit(x)))
nan_mean <- function(x) mean(na.omit(x))
df.summary.followup <- post_TD %>%
  group_by(attention_state,TD_within_triplet_counter) %>%
  dplyr::summarise(
    se_rt = nan_se(TD_rt),
    mean_rt = nan_mean(TD_rt),
  )
df.summary.followup <- na.omit(df.summary.followup)
df.summary.followup

#sanity check: ungroup function
# df.summary.followup_ung <- post_TD %>%
#   group_by(attention_state,TD_within_triplet_counter) %>%
#   dplyr::summarise(
#     se_rt = nan_se(TD_rt),
#     mean_rt = nan_mean(TD_rt),
#   ) %>% 
#   ungroup()
# df.summary.followup_ung <- na.omit(df.summary.followup_ung)
# df.summary.followup_ung
```




```{r}
df.summary.followup.resid <- post_TD_nonan %>%
  group_by(attention_state,TD_within_triplet_counter) %>%
  dplyr::summarise(
    se_resid = nan_se(resid_from_stream),
    mean_resid = nan_mean(resid_from_stream),
  )
df.summary.followup.resid
```


```{r}
# old color c(#531a74,#305614)
p1 <- ggplot(df.summary.followup, aes(TD_within_triplet_counter, mean_rt, ymin = mean_rt-se_rt, ymax = mean_rt+se_rt, group=attention_state)) +
  geom_line(aes(color=attention_state),size=1.2) +
  geom_pointrange(aes(color=attention_state)) +
  geom_errorbar(aes(color=attention_state), width = 0.06) +
  scale_color_manual(values=c("#682191","#508f22"), labels = c("low attentional state", "high attentional state")) +
  theme_classic() + theme(aspect.ratio = 0.8,legend.position="top", axis.text.y=element_text(size=10, colour="black"), axis.text.x=element_text(size=10, colour="black"),axis.title.y=element_text(size=10),axis.title.x=element_text(size=10),legend.direction = "vertical", legend.text=element_text(size=10)) +
  labs(x = " ", y = "RT (ms)", color = "") +
  scale_x_discrete(expand = c(0,0.2), breaks=c("1","2","3"), labels=c("first \n triplet position", "second \n triplet position", "third \n triplet position")) +
  ylim(360,420) 

#ggsave("Fig3b.png", width = 5.5, height = 4, dpi=300)
p1
```


```{r}
p2 <- ggplot(df.summary.followup.resid, aes(TD_within_triplet_counter, mean_resid, ymin = mean_resid-se_resid, ymax = mean_resid+se_resid, group=attention_state)) +
  geom_line(aes(color = attention_state),size=1.2) +
  geom_pointrange(aes(color = attention_state)) +
  geom_errorbar(aes(color= attention_state), width = 0.06)+
  scale_color_manual(values=c("#682191","#508f22") , labels = c("low attentional state", "high attentional state")) +
  theme_classic() + theme(aspect.ratio = 0.8,legend.position="top", axis.text.y=element_text(size=10, colour="black"), axis.text.x=element_text(size=10, colour="black"),axis.title.y=element_text(size=10),axis.title.x=element_text(size=10),legend.direction = "vertical", legend.text=element_text(size=10)) +
  labs(x = " ", y = "residual", color = "") +
  scale_x_discrete(expand = c(0,0.2), breaks=c("1","2","3"), labels=c("first \n triplet position", "second \n triplet position", "third \n triplet position")) +
  ylim(-20,20)
#ggsave("Fig3d.png", width = 5.5, height = 4, dpi=300)
p2
```


# Post-hoc analyses on the two-way interaction between experiments
## Non-parametric: Bootstrap on experiments

```{r}
df_ordered$exp <- rep('E1a',nrow(df_ordered))
post_TD_nonan$exp <- rep('E1b',nrow(post_TD_nonan))

names(df_ordered)[names(df_ordered) == "within_triplet_counter"] <- "TD_within_triplet_counter"
names(df_ordered)[names(df_ordered) == "within_stream_position"] <- "TD_target_position"

names(df_ordered)
df_ordered
names(post_TD_nonan)
```

```{r}
df_ordered_withDD <- df_ordered %>% subset(!(participant %in% c("ba694","6662c")))
df_all <- rbind(df_ordered_withDD[,c("TD_within_triplet_counter","attention_state","participant","TD_rt","TD_target_position","resid_from_stream","exp")],post_TD_nonan[,c("TD_within_triplet_counter","attention_state","participant","TD_rt","TD_target_position","resid_from_stream","exp")])

# length(unique(df_all$participant))
# length(unique(post_TD_nonan$participant))
# length(unique(df_ordered_withDD $participant))
df_all
```


```{r}
# chi_sqrt_E1a <- 12.07
# chi_sqrt_E1b <- 3.41

run_model <- function(data) {
  #build model and obtain chi-squared value
  model_5_followup = lmer(resid_from_stream ~ TD_within_triplet_counter * attention_state + (attention_state + TD_within_triplet_counter|participant), data=data)
  sample_chi_sqrt <- Anova(model_5_followup)[3,"Chisq"]
  return(sample_chi_sqrt)
}

get_boot_mean <- function(data) {
  #sample people with replacement
  boot_sample = data %>% 
      group_by(participant) %>% #group by participant
      sample_frac(1, replace=TRUE)
  chi_sqrt <- run_model(boot_sample) # return just the values so replicate can return a matrix
  
  return(chi_sqrt)
}

```


### E1a
```{r}
get_boot_mean(df_ordered_withDD)
```


### E1b
```{r message=FALSE, warning=FALSE}
# options(warn=-1)
get_boot_mean(post_TD_nonan)
```

```{r message=FALSE, warning=FALSE}
#build distribution
options(warn=-1)
boot_chi_sqrt_E1a <- replicate(1000, get_boot_mean(df_ordered_withDD))
# boot_chi_sqrt_E1a[,1:5]
```



```{r message=FALSE, warning=FALSE}
#build distribution
options(warn=-1)
boot_chi_sqrt_E1b <- replicate(1000, get_boot_mean(post_TD_nonan))
# boot_chi_sqrt_E1b[,1:5]

```

```{r}
boot_chi_sqrt_E1a[1:5]
boot_chi_sqrt_E1b[1:5]

#write.csv(boot_chi_sqrt_E1a,'/Users/ziweizhang/Downloads/Stats_lr_trig_data/analysis_output/E2/boot_chi_sqrt_E1_final.csv', row.names = FALSE)
#write.csv(boot_chi_sqrt_E1b,'/Users/ziweizhang/Downloads/Stats_lr_trig_data/analysis_output/E2/boot_chi_sqrt_E2_final.csv', row.names = FALSE)
```



```{r}
(median(boot_chi_sqrt_E1a))  # sample chi sqrt means
(median(boot_chi_sqrt_E1b))  # sample chi sqrt means

quantile(boot_chi_sqrt_E1a, probs = c(0.025, 0.975))  # 95% CI for age 5
quantile(boot_chi_sqrt_E1b, probs = c(0.025, 0.975))  # 95% CI for age 3
```



```{r}
#see if one median is within the CI of the other
#if the null distribution is E1b, compare with the median of E1a
coeff_mean_E1a <- mean(boot_chi_sqrt_E1a)
coeff_median_E1a <- median(boot_chi_sqrt_E1a)
coeff_mean_E1a
coeff_median_E1a

# one-tailed p
((1 + sum(coeff_mean_E1a <= boot_chi_sqrt_E1b)) / (1001))

# two-tailed p
((1 + sum(abs(coeff_median_E1a) <= abs(boot_chi_sqrt_E1b))) / (1001))

```


```{r}
#another way
ecdf_fun <- function(x,perc) ecdf(x)(perc)
greater_tail_quantile <- (1 - ecdf_fun(boot_chi_sqrt_E1b,coeff_median_E1a))
greater_tail_quantile

less_tail_value <-quantile(boot_chi_sqrt_E1b, probs = (1-greater_tail_quantile))
less_tail_quantile <- (1 - ecdf_fun(boot_chi_sqrt_E1b,less_tail_value))
less_tail_quantile

two_tailed_p <- less_tail_quantile + greater_tail_quantile
two_tailed_p
```


```{r}
#see if one median is within the CI of the other
#if the null distribution is E1a, compare with the median of E1b
coeff_mean_E1b <- mean(boot_chi_sqrt_E1b)
coeff_median_E1b <- median(boot_chi_sqrt_E1b)
coeff_mean_E1b
coeff_median_E1b

# one-tailed p
((1 + sum(coeff_median_E1b >= boot_chi_sqrt_E1a)) / (1001))

# two-tailed p
((1 + sum(abs(coeff_median_E1b) <= abs(boot_chi_sqrt_E1a))) / (1001))

```

```{r}
ecdf_fun <- function(x,perc) ecdf(x)(perc)
less_tail_quantile <- ecdf_fun(boot_chi_sqrt_E1a,coeff_median_E1b)
less_tail_quantile

greater_tail_value <- quantile(boot_chi_sqrt_E1a, probs = (1- less_tail_quantile))
greater_tail_quantile <- (1 - ecdf_fun(boot_chi_sqrt_E1a,greater_tail_value))
greater_tail_quantile

two_tailed_p <- less_tail_quantile + greater_tail_quantile
two_tailed_p
```


```{r}
#report independent cohen's d
cohen_d <- function(samp1, samp2){
  m1 <- mean(samp1)
  m2 <- mean(samp2)
  n1 <- length(samp1)
  n2 <- length(samp2)
  sd1 <- sd(samp1)
  sd2 <- sd(samp2)

  samp1_sd <- (n1-1)*sd1^2
  samp2_sd <- (n2-1)*sd2^2

  sd_pooled <- sqrt( (samp1_sd + samp2_sd) / (n1+n2-2)  )
  cohen_d <- (m1 - m2) / sd_pooled

  return(cohen_d)
}
cohen_d(boot_chi_sqrt_E1a, boot_chi_sqrt_E1b)
```


```{r}
boot_chi_sqrt_plot <- data.frame(boot_chi_sqrt = c(boot_chi_sqrt_E1a, boot_chi_sqrt_E1b), exp = rep(c("E1","E2"),each = length(boot_chi_sqrt_E1b)))
boot_chi_sqrt_plot$exp <- as.factor(boot_chi_sqrt_plot$exp)

cutoff <- data.frame( x = coeff_median_E1a, y = c(-Inf, Inf), E1_median = factor(round(coeff_median_E1a, digits = 2)))

p5 <- ggplot(boot_chi_sqrt_plot,aes(x=boot_chi_sqrt, fill=exp)) +
    geom_histogram(alpha=0.7, bins = 35, color="#B4B4B4") +
    scale_fill_manual(values=c("dark gray","light gray"), labels = c("E1", "E2")) +
    geom_vline(aes(xintercept = x, color = E1_median), size=0.8, data = cutoff,key_glyph = "path" ) +
    scale_color_manual(values = c('firebrick2'), labels = c("E1 median")) +
    theme_classic() + theme(aspect.ratio = 0.8, legend.position="right", axis.text.y=element_text(size=14), axis.text.x=element_text(size=14), axis.title.y=element_text(size=14),axis.title.x=element_text(size=14), legend.direction = "vertical", legend.text=element_text(size=14),legend.title=element_blank()) +
  labs(x = "chi-squared bootstrap value", y = "count", fill = "") +
  ylim(0,200) + xlim(0,52)
p5
#ggsave("boot_dist_E1_E2_final.pdf", width = 5.5, height = 4, dpi=300)
```



```{r}
#one distribution with median
boot_chi_sqrt_E1b_plot <- data.frame(boot_chi_sqrt =  boot_chi_sqrt_E1b, E2 = rep(c("E2"), each = length(boot_chi_sqrt_E1b)))

cutoff <- data.frame( x = coeff_median_E1a_null, y = c(-Inf, Inf), E1_median = factor(round(coeff_median_E1a_null, digits = 2)))
      
p6 <- ggplot(boot_chi_sqrt_E1b_plot, aes(x = boot_chi_sqrt, fill=E2)) +
  geom_histogram(color="#B4B4B4", alpha=0.7, bins = 35) +   #geom_vline(xintercept = coeff_median_E1a_null, color='firebrick2', size=0.8) + 
  scale_fill_manual( values="light gray", labels = "") +
  #geom_line(aes( x, y, linetype = E1_median), cutoff, color='firebrick2', size=0.8 ) +
  geom_vline(aes(xintercept = x, linetype = E1_median), color='firebrick2', size=0.8, data = cutoff, show.legend=TRUE) +
  #scale_color_manual(values = c('firebrick2'), labels = c("E1 median")) +
  labs(x="chi-squared bootstrap value", y="count", fill="E2") + theme_classic() + theme(aspect.ratio = 0.8, axis.text.x = element_text(size=14), axis.text.y = element_text(size=14), axis.title.x=element_text(size=14), axis.title.y=element_text(size=14), legend.position="right", legend.direction = "vertical") +
  ylim(0,200) + xlim(0,52)
 
#ggsave("boot_p_val.pdf", width = 5.5, height = 4, dpi=300)
p6
```


## t-test on third position RT
```{r}
third_mean <- df_all %>% subset(TD_within_triplet_counter == "2" | TD_within_triplet_counter == "3")
third_mean
third_mean <- third_mean %>% group_by(TD_within_triplet_counter,attention_state,participant) %>%
  dplyr::summarise(
    mean_third = nan_mean(TD_rt),
    mean_third_resid = nan_mean(resid_from_stream),
    exp = exp[1]
  )
third_mean
```

```{r}
# df_all %>% group_by(exp,attention_state,participant) %>%
#   dplyr::summarise(
#     count = n()
#   )
length(unique(third_mean$participant))
length(unique(df_all$participant))

third_mean %>% group_by(attention_state,exp) %>%
  dplyr::summarise(
    count = n()
  )

#we know that in E1a we're missing three people who don't have data for high atten trials at the third position

E1a_slow <- third_mean %>% subset(exp == "E1a" & attention_state == "slow")
length(unique(E1a_slow$participant))

third_mean_include <- third_mean %>% subset(participant %in% unique(E1a_slow$participant) | exp == "E1b")
third_mean_include

```


```{r}
# third_diff_include <- third_mean_include %>% group_by(participant) %>%
#    mutate(Diff = mean_third - lag(mean_third))

third_mean_include_E1a <- third_mean_include %>% subset(exp == "E1a")
third_mean_include_E1b <- third_mean_include %>% subset(exp == "E1b")
third_mean_include_E1a
third_mean_include_E1b

third_mean_include_E1a %>% group_by(attention_state,participant) %>%
  dplyr::summarise(
    count = n()
  )
```

```{r}
third_diff_include_E1a <- third_mean_include_E1a %>%
  pivot_wider(names_from = c(attention_state,TD_within_triplet_counter),
              values_from = mean_third_resid,
              names_sep = ".",
              id_cols = participant) %>%
  mutate(diff_third_resid = fast.3 -slow.3,
         diff_second_resid = fast.2 -slow.2,
         diff_resid = diff_third_resid - diff_second_resid,
         diff_third_resid_z = (diff_third_resid - mean(diff_third_resid))/sd(diff_third_resid)
         )
third_diff_include_E1a
```

```{r}
# third_diff_include_E1b <- third_mean_include_E1b %>%
#   pivot_wider(names_from = attention_state,
#               values_from = mean_third_resid,
#               id_cols = participant) %>%
#   mutate(diff_third_resid = fast -slow,
#          diff_third_resid_z = (diff_third_resid - mean(diff_third_resid))/sd(diff_third_resid)
# )
# third_diff_include_E1b

third_diff_include_E1b <- third_mean_include_E1b %>%
  pivot_wider(names_from = c(attention_state,TD_within_triplet_counter),
              values_from = mean_third_resid,
              names_sep = ".",
              id_cols = participant) %>%
  mutate(diff_third_resid = fast.3 -slow.3,
         diff_second_resid = fast.2 -slow.2,
         diff_resid = diff_third_resid - diff_second_resid,
         diff_third_resid_z = (diff_third_resid - mean(diff_third_resid))/sd(diff_third_resid)
         )
third_diff_include_E1b
```


```{r}
diff_E1a <- third_diff_include_E1a$diff_resid
diff_E1b <- third_diff_include_E1b$diff_resid
t.test(diff_E1a, diff_E1b)
```

```{r}
hist(third_diff_E1a)
hist(third_diff_E1b)
```


## Parametric: https://link.springer.com/content/pdf/10.1007/BF02289361.pdf
```{r}
chi_sqrt_E1a <- 12.07
chi_sqrt_E1b <- 3.41

delta_chi_squared <- 0.5*(chi_sqrt_E1a^2 - chi_sqrt_E1b^2)
delta_chi_squared
Bessel_func <- function(x) {
  1/sqrt(pi) * 1/(2^148) * 1/rgamma(1, 148+0.5) * delta_chi_squared^148 * K_func()
  
} 
```


# Sanity check
```{r}
post_TD$TD_within_triplet_counter <- as.numeric(post_TD$TD_within_triplet_counter)
post_TD %>% group_by(participant,attention_state) %>% 
  dplyr::summarise(mean_target=mean(TD_target_position), mean_within_coutner=mean(TD_within_triplet_counter))
```


# Drag and Drop
```{r}
length(sub_id_collected)
length(unlist(yoke_id_collected))
length(yoke_id_template)
```

```{r}
recreate
```



```{r}
# test_part with post_TD tag are the trials of interests
post_DD = data_all %>% subset(test_part == 'post_drag')

recreate = post_DD[,c('participant','rt','init_locations','final_locations','trial_type')]
recreate$participant <- rep(na.omit(sub_id_collected), each=2)
recreate$yoke_participant <- rep(unlist(yoke_id_collected),each=2)

recreate
```

```{r}
recreate  <- recreate[order(recreate$yoke_participant),]
recreate_template  <- recreate_template[order(recreate_template$yoke_participant_template),]
recreate_final <- cbind(recreate, recreate_template)   
recreate_final
```

### create csv file for python script
```{r}
#write.csv(recreate_final,'/Users/ziweizhang/Downloads/Stats_lr_trig_data/analysis_output/E2/recreate_followup.csv', row.names = FALSE)
```


# Awareness question
```{r}
question = data_all %>% subset(is.na(responses) ==  F)
question
```

```{r}
participant_list <-na.omit(unique(question$participant))

#take participant and make them the entire column
question$participant <- rep(participant_list, each = 3)
question
```


```{r}

#Q1_FR: stratergy
stratergy <- question %>% subset(trial_index ==  61)

#Q2_FR: pattern
pattern_noticed <- question %>% subset(trial_index ==  62)


#Q3_MC: awareness and Q4_MC: attention check
#select where participant is not nan
#attention_check = question %>% subset(is.na(participant) ==  F)
awareness_attention <- question %>% subset(trial_index ==  66)
awareness_attention
```

```{r}
answer_attention_list <- rep(NA, 148)
answer_awareness_list <- rep(NA, 148)
```


```{r}
#test_string <- toString(awareness_attention$responses[1])
awareness_attention$responses_string <- lapply(awareness_attention$responses, toString)
# df[2] <-
awareness_attention
awareness_attention$responses_string
```

```{r}
check_awareness <- function(x) {
  if (toString(x)== "\"Yes\"") {
    awareness <- 1
  } else {awareness <- 0}
  return(awareness)
}  
# print(toString(answer_awareness[2])== "\"Yes\"")
# check_awareness(answer_awareness[2])

check_attention <- function(x) {
  if (toString(x)== "\"Press SPACEBAR to a target\"}") {
    attention <- 1
  } else {attention <- 0}
  return(attention)
}  
# print(toString(answer_attention[2])== "\"Press SPACEBAR to a target\"}")
# check_attention(answer_attention[2])
```


```{r}
#function to separate the string for each subject into 2 questions
sep_question_awareness <- function(x) {
  string_by_question <- as.list(strsplit(x, ",")[[1]])
  string_awareness <- toString(string_by_question[1])
  answer_awareness <- as.list(strsplit(string_awareness, ":")[[1]])
  answer_awareness_num <- check_awareness(answer_awareness[2])
  return(answer_awareness_num)
}

awareness_attention$test_awareness <- unlist(lapply(awareness_attention$responses_string, sep_question_awareness))
awareness_attention

# string_by_question <- as.list(strsplit(test_string, ",")[[1]])
# string_by_question
# 
# string_awareness <- toString(string_by_question[1])
# string_attention <- toString(string_by_question[2])
# 
# answer_awareness <- as.list(strsplit(string_awareness, ":")[[1]])
# answer_awareness
# 
# answer_attention <- as.list(strsplit(string_attention, ":")[[1]])
# answer_attention
```


```{r}
#function to separate the string for each subject into 2 questions
sep_question_attention <- function(x) {
  string_by_question <- as.list(strsplit(x, ",")[[1]])
  string_attention <- toString(string_by_question[2])
  answer_attention <- as.list(strsplit(string_attention, ":")[[1]])
  answer_attention_num <- check_attention(answer_attention[2])
  return(answer_attention_num)
}

awareness_attention$test_attention <- unlist(lapply(awareness_attention$responses_string, sep_question_attention))
awareness_attention
```


```{r}
sum(awareness_attention$test_awareness)
sum(awareness_attention$test_attention)
```


### awareness question by learners
```{r}
both_learner_awareness_attention <- awareness_attention %>% subset(participant %in% both_learner$participant)
high_at_learner_awareness_attention <- awareness_attention %>% subset(participant %in% high_at_learner$participant)
low_at_learner_awareness_attention <- awareness_attention %>% subset(participant %in% low_at_learner$participant)
none_learner_awareness_attention <- awareness_attention %>% subset(participant %in% none_learner$participant)
learner_awareness_attention <- awareness_attention %>% subset(participant %in% learner$participant)
```


```{r}
print(c("number of both learner is", nrow(both_learner), "number with awareness is", sum(both_learner_awareness_attention$test_awareness)))#, "and they are", both_learner_awareness_attention$participant)
```


```{r}
print(c("number of high attention learner is", nrow(high_at_learner), "number with awareness is",
sum(high_at_learner_awareness_attention$test_awareness))) # , "and they are", high_at_learner_awareness_attention$participant)
```

```{r}
print(c("number of low attention learner is", nrow(low_at_learner), "number with awareness is",
sum(low_at_learner_awareness_attention$test_awareness))) # , "and they are", low_at_learner_awareness_attention$participant)
```

```{r}
print(c("number of none learner is", nrow(none_learner), "number with awareness is",
sum(none_learner_awareness_attention$test_awareness))) # , "and they are", none_learner_awareness_attention$participant)
```


```{r}
print(c("number of learner is", nrow(learner), "number with awareness is",
sum(learner_awareness_attention$test_awareness))) # , "and they are", learner_awareness_attention$participant)
```

